\LARGE \bf Dex-Net 1.0: A Cloud-Based Network of 3D Objects and Parallel-Jaw Grasps and a Multi-Armed Bandit Algorithm with Correlated Rewards for Robust Grasp Planning at Scale \versionline{4}

### 2015-09-10 ICRA2016/bandits_docs/includes/problem_statement.tex
Modified entire draft. In a limbo state. Going back through feedback now.

\TODO{Fill in more details. This is a stripped down version to get ideas down on the page}
Let $\bg = [\bx, \bw]^T$ be a parallel-jaw grasp parameterized by its center in 3D space $\bx \in \mathbb{R}^3$ and approach direction $\bv \in \mS^2$.
Let $\mG = \{ [\bx, \bw]^T \big| \bx \in \mathbb{R}^3,  \}$ denote the space of all grasps.
%We will assume a fixed set of candidate grasps $\Gamma = \{ g_1, ..., g_N\}$.
%Ideally the candidate set would form a cover of the which may be generated via Gaussian pose sampling~\cite{} or heur.

We will assume a known object shape $\nu$, and known uncertainty in object pose, gripper pose, and friction coefficient resulting from sensing uncertainties and missing data following the model of Laskey et al.~\cite{laskey2015bandits}. 
%Let $\upsilon$ be a random variable representing object shape represented by a Gaussian Process implicit surface~\cite{} distribution over signed distance fields $f$ with mean $\mu_f \in \mathbb{R}^{M \times M}$ and covariance $\Sigma_f$.
Let $\xi$ be uncertainty in object pose distributed as a Gaussian with mean $\mu_{\xi} \in \mathfrak{se}(3)$ and covariance $\Sigma_{\xi}$.
Let $\rho$ be uncertainty in gripper pose distributed as a Gaussian with mean $\mu_{\rho} \in \mG$ and covariance $\Sigma_{\rho}$.
Let $\zeta$ denote uncertiainty in friction coefficient distributed as a Gaussian with mean $\mu_{\zeta} \in \mathbb{R}$ and covariance $\Sigma_{\zeta}$.
Given object shape and samples of object pose, and gripper pose, we let $\bc_i(\bg, \theta, \xi, \rho) \in \mathbb{R}^3$ for $i \in {1, 2}$ denote the 3D location of contact between the $i$-th gripper jaw and surface.
Furthermore, let $\bn_i(\bc_i, \nu) \in \mS^2$ denote the surface normal at this contact.
A graphical model describing the relationship between these quantities is given in~\figref{graphical-model}.

We measure grasp quality by the probability of force closure subject to these uncertain quantities.
Let $F \in \{0, 1\}$ denote the occurence of force closure, or the ability to resist wrenches in arbitrary directions~\cite{ferrari1992}.
Then the probability of force closure for a grasp $\bg$ is
%\vspace{-2ex}
\begin{align*}
	P_F(\bg) = \mathbb{P}\left(F = 1 \mid \bg, \xi, \rho, \zeta \right).
\end{align*}
\noindent We are interested in finding the candidate grasp that maximizes the probability of force closure $P_F(g)$~\cite{kim2012physically, laskey2015bandits, mahler2015gp, weisz2012pose} subject to these sources of uncertainty over a budgeted maximum number of samples $T$.
To perform this as q	uickly as possible we formulate this as a maximization over the sum of the true $P_F$ for the grasps sampled at iteration $t$, where $I(i)$ denotes the grasp selected at time $t$

\vspace{-2ex}
\begin{align}
	\maximum{g_{I(1)}, ..., g_{I(T)} \in \mG} \sum \limits_{t=1}^T P_F(g_{I(t)}) \label{eq:objective}
\end{align}

\noindent As the maximization over the continuous space $\mG$ is computationally expensive, past work has solved this objective using a discrete set of $K$ candidate grasps $\Gamma = \left\{ \bg_1, ..., \bg_K \right\}$.
In practice $\Gamma$ has been set using Gaussian sampling of grasp centers and poses~\cite{laskey2015bandits} or using heuristics such as antipodality~\cite{mahler2015opt}.
\TODO{Switch to task-based quality metric (e.g. resiting gravity)? I think it would be more compelling but doesn't seem to have much precedent}

Even with a discrete set of candidates, evaluating $P_F(\bg)$ for any grasp requires an expensive integration over possible contact locations between the grasp and surface and the surface normals at these contacts~\cite{mahler2015gp}.
Thus, past work has evaluated the probability of force closure using Monte-Carlo integration~\cite{kehoe2012estimating, kehoe2012toward, weisz2012pose}, approximating the expression by minimzing uncertainty at the contact locations~\cite{mahler2015gp}, and using Multi-Armed Bandit algorithms to jointly evaluate $P_F(\bg)$ using Monte-Carlo integration while allocating samples to more promising grasps.
In this work, we propose to use Multi-Armed Bandits with correlations between arms to further accelerate convergence.

>>>>

Given a previously unknown object, we consider the problem of finding a of parallel-jaw grasps with maximum probability force closure, $P_F$, under uncertainty in object pose, gripper pose, and friction coefficient using a database of 3D object models annotated with grasps and the $P_F$ of each.
We assume the object shape is exactly known and provided as a signed distance function (SDF) $f: \mathbb{R}^3 \rightarrow \mathbb{R}$~\cite{mahler2015gp, newcombe2011kinectfusion}, which is zero on the object surface, positive outside the object, and zero inside the object. 
We also assume that the object is specified in units of meters and the object center of mass $\bz \in \mathbb{R}^3$ is known.
Furthermore, we assume soft-finger contacts between the gripper and object~\cite{zheng2005} and that the gripper jaws are opened to their maximal width $w \in\bR$ before closing on the object.
%and known uncertainty in object pose, gripper pose relative to the object, and friction coefficient, described in detail in \seclabel{uncertainty} below.

\subsection{Grasp and Object Parameterization}
\seclabel{grasp-param}
Our grasping parameterization is illustrated in~\figref{grasp-model}.
Let $\bg = (\bx, \bv)^T$ be a parallel-jaw grasp parameterized by the centroid of the jaws in 3D space $\bx \in \mathbb{R}^3$ and an approach direction, or axis, $\bv \in \bS^2$.
Let $f: \mathbb{R}^3 \rightarrow \mathbb{R}$ be a signed distance function (SDF) representing an object's geometry~\cite{mahler2015gp, newcombe2011kinectfusion}.
We denote by $\mS = \{\by \in \bR^3 \big| f(\by) = 0\}$ the surface of an object, and assume that all points are specified with respect to a reference frame centered at the object center of mass $\bz$ and oriented along the principal axes of $\mS$.
Let $\mG = \{ [(\bx, \bw) \big| \bx \in \mathbb{R}^3, \bv \in \bS^2\}$ denote the space of all grasps and $\mH = \{ \mO = \{\bz, f(\cdot)\} \big|  \bz \in \mathbb{R}^3, f \in \mF\}$ denote the space of all objects, where the $\mF$ is the space of all SDFs.
We denote by $\mM = \mG \times \mH$ the joint space of all parallel-jaw grasps and objects, also known as a Grasp Moduli Space~\cite{pokorny2013grasp}.

\begin{figure}[t!]
\centering
\includegraphics[scale=0.4]{figures/illustrations/dexnet_grasping_model.png}
\caption{Illustration of our grasp parameterization and contact model. (Left) We parameterize parallel-jaw grasps by the centroid of the jaws $\bx \in \mathbb{R}^3$ and approach direction, or direction along which the jaws close, $\bv \in \bS^2$. The grasp parameters $\bx$ and $\bv$ are specified with respect to a coordinate frame located at the object center of mass $\bz$ and oriented along the principal directions of the object. (Right) The jaws are closed until contacting the object surface at locations $\bc_1, \bc_2 \in \mathbb{R}^3$, at which the surface has normals $\bn_1, \bn_2 \in \bS^2$. The contacts are used to compute the moment arms $\rho_1 = \bc_1 - \bz$ and $\rho_2  = \bc_2 - \bz$. From these parameters we can derive the forces and torques that the gripper can apply to the object. }
\figlabel{grasp-model}
\vspace*{-15pt}
\end{figure}

%Let $\mM = \left\{\mV, \mT \right\}$ be a triangular mesh representing an object's geometry, where $\mV = \{\bw_i \in \mathbb{R}^3 \}_{i=1}^{N_v}$ is a set of $N_v$ vertices and $\mT = \{ \bt_i \in \mathbb{Z}_{+}^3 \}_{i=1}^{N_t}$ is a set of $N_t$ triangles formed by triplets of integer indices of vertices.
%We will assume a fixed set of candidate grasps $\Gamma = \{ g_1, ..., g_N\}$.
%Ideally the candidate set would form a cover of the which may be generated via Gaussian pose sampling~\cite{} or heur.

\subsection{Sources of Uncertainty}
\seclabel{uncertainty}
We assume Gaussian uncertainty in 3D object pose, gripper pose, and friction coefficient resulting from sensing uncertainties and missing data extended from the 2D model of Laskey et al.~\cite{laskey2015bandits}.
Let $\upsilon \sim \mN\left(\mathbf{0}, \Sigma_{\upsilon}\right)$ be a zero-mean Gaussian on $\bR^6$ and $\mu_{\xi} \in SE(3)$ be a mean object pose.
Following the model of Barfoot and Furgale~\cite{barfoot2014associating}, we define the object pose random variable $\xi = \exp\left( \upsilon^{\wedge} \right) \mu_{\xi}$, where the $\wedge$ operator maps from $\bR^6$ to the Lie algebra $\mathfrak{se}(3)$.
Let $\nu \sim \mN\left(\mu_{\nu}, \Sigma_{\nu}\right)$ denote Gaussian uncertainty in gripper pose with mean $\mu_{\nu} \in \mG$.
Let $\gamma \sim \mN\left(\mu_{\gamma}, \Sigma_{\gamma} \right)$ denote Gaussian uncertainty in friction coefficient distributed as a Gaussian with mean $\mu_{\gamma} \in \mathbb{R}$.
We denote by $\hat{\xi}, \hat{\nu},$ and $\hat{gamma}$ samples of object pose, gripper pose, and friction, respectively. 
%Theses sources of uncertainty might be estimated based on prior models of repeatability in gripper actuation or from the posterior variance in object pose or friction coefficient in estimates based on sensor data.

\subsection{Contact Model}
\seclabel{contact}
Our contact model is illustrated in the right panel of \figref{grasp-model}.
Given a grasp $\bg$ with width $w$ on an object $\mO$ and samples of object pose, gripper pose, and friction, let $\bc_i \in \mathbb{R}^3$ for $i \in {1, 2}$ denote the 3D contact location between the $i$-th gripper jaw and surface.
Each contact $\bc_i = \bx + s_i (t_i^* - w / 2) \bv$ where
\begin{align*}
	t_i^* &= \minimum{t \geq 0} t \text{ such that } f\left(\bx + s_i (t - w / 2) \bv\right) = 0,
\end{align*}
\noindent$s_1 = -1$, and $s_2 = 1$~\cite{mahler2015gp}.

Given contact points, let $\bn_i = \nabla f(\bc_i) / \| \nabla f(\bc_i) \|_2$ denote the surface normal at contact $\bc_i$ with tanget vectors $\bt_{i,1}, \bt_{i,2} \in \bS^2$.
To compute the forces that each contact can apply to the object for a sampled friction coefficient $\hat{\gamma}$, we discretize the friction cone at contact $i$~\cite{pokorny2013classical} into a discrete set of $l$ facets with vertices $\mF_{i} = \left\{ \bbf_{i,j} = \bn_i + \hat{\gamma} \cos \left( \frac{2 \pi j}{l} \right) \bt_{i,1} + \hat{\gamma} \sin \left( \frac{2 \pi j}{l} \right) \bt_{i,2} \text{ for } j = 1, ..., l \right\}$.
Each force $\bbf_{i,j}$ can exert a corresponding torque $\tau_{i,j} = \bbf_{i,j} \times \rho_i$ where $\rho_i = (\bc_i - \bz)$ is the moment arm at contact $i$.
Under our soft contact model, each contact $\bc_i$ exerts an additional wrench $\bw_{i,l+1} = (\mathbf{0}, \bn_i)$~\cite{zheng2005}.
Thus the set of all wrenches that can be applied by a grasp $\bg$ under our model is $\mW = \{ \bw_{i,j} = (\bbf_{i,j}, \tau_{i,j}) \big| i = 1, 2 \text{ and } j = 1, ..., l+1\}$.

\subsection{Quality Metric}
\seclabel{quality}
In this work we use force closure, or the ability to resist external force and torques in arbitrary directions~\cite{ferrari1992}, as our grasp success metric.
While we acknowledge that some evidence suggests that deterministic force closure is not always a strong predictor of physical grasp success~\cite{balasubramanian2012physical, diankov2010automated}, we use the probability of force closure because of it has shown promise in physical experiments~\cite{kim2012physically, weisz2012pose}, and it is relatively inexpensive to evaluate when compared to human labels or physical executions, allowing us to better study the effects of large amounts of data.

Let $F \in \{0, 1\}$ denote the occurence of force closure.
To compute force closure for a grasp $\bg \in \mG$ on object $\mO \in \mH$ given samples of object pose $\xi$, gripper pose $\nu$, and friction coefficient $\gamma$, we first compute the set of possible contact wrenches $\mW$.
Then $F = 1$ if the origin lies within the convex hull of the contact wrench set, $\mathbf{0} \in Conv(\mW)$~\cite{weisz2012pose}.
%A graphical model describing the relationship between these quantities is given in~\figref{graphical-model}.
%
%\begin{figure}[t!]
%\centering
%\includegraphics[scale=0.5]{figures/illustrations/dexnet_graphical_model_simple.png}
%\caption{A graphical model describing the relationships between known uncertain parameters (shaded gray) such as object pose and the force closure random variable $F$.}
%\figlabel{graphical-model}
%\vspace*{-15pt}
%\end{figure}

\subsection{Objective}
The probability of force closure for a grasp $\bg$ on object $\mO$ is $P_F(\bg, \mO) = \mathbb{P}\left(F = 1 \mid \bg, \mO, \xi, \nu, \gamma \right)$.
We are interested in finding $\bg^*$,the grasp that maximizes the probability of force closure $P_F(g)$~\cite{kim2012physically, laskey2015bandits, mahler2015gp, weisz2012pose} over a budgeted maximum number of samples $T$.
To perform this as quickly as possible we maximize over the sum of the $P_F$ for all sampled grasps~\cite{laskey2015bandits, srinivas10gaussian}:

\vspace{-2ex}
\begin{align}
	\underset{g_{I(1)}, ..., g_{I(T)} \in \mG}{\text{maximize }} \sum \limits_{t=1}^T P_F(g_{I(t)}). \label{eq:objective}
\end{align}
\noindent where $I(i)$ denotes the grasp selected at time $t$.

As the maximization over the continuous space $\mG$ is computationally expensive, past work has solved this objective by evaluating a discrete set of $K$ candidate grasps $\Gamma = \left\{ \bg_1, ..., \bg_K \right\}$ with Monte-Carlo integration~\cite{kehoe2012toward, weisz2012pose} or Multi-Armed Bandits(MAB) ~\cite{laskey2015bandits}.
In this work, we extend the MAB model of~\cite{laskey2015bandits} to 3D and to leverage similarities between grasps and prior objects in Dex-Net for accelerated convergence to $\bg^*$.

### 2015-09-10 ICRA2016/bandits_docs/includes/related_work.tex
Modified entire draft. In a limbo state. Going back through feedback now.

For a survey of the substantial literature on grasping, see Prattichizzo and Trinkle~\cite{prattichizzo2008grasping}.
Research on grasp planning has focused on finding grasps by maximizing an analytic grasp quality metric based on wrench space (WS), such as the ability to resist external perturbations to the object based on the grasp WS~\cite{ferrari1992, miller2004graspit}, object WS~\cite{liu2015fast, pollard1994parallel}, or task WS~\cite{kruger2011partial, li1988task}.
WS metrics have been used to synthesize grasps for known objects using sampling-based optimization in software tools such as GraspIt!~\cite{miller2004graspit} or OpenGRASP~\cite{leon2010opengrasp}.
However, analytic WS metrics have been criticized~\cite{balasubramanian2012physical, weisz2012pose} for not being robust to variations in grasp acquistion, such as object shape, pose, material properties, and locations of contact~\cite{cheong2011output, diankov2010automated, weisz2012pose, zheng2005} and for not taking into account the dynamics of the the grasp~\cite{prattichizzo2008grasping}.
%This has motivated work on grasp transfer from a knowledge database to new objects, robust versions of analytic quality metrics with respect to uncertainty in the state of the robot and environment, and synthesis from statistical models of grasping learned from physical data or human labels.

The need to recompute WS metrics to select grasps for every new object motivated research on grasp synthesis by transferring grasps from a database of exemplar objects.
Li and Pollard~\cite{li2005shape} generated grasps by matching object shapes to human hand postured in a database.
Goldfelder et al.~\cite{goldfeder2009columbia} developed the Columbia grasp database, a database of 1,814 distinct models and over 200,000 force closure grasps generated using the Eigengrasp planner in GraspIt!~\cite{ciocarlie2009}.
The authors later used synthetic partial depth maps of objects in the database to match robot sensor data to precomputed grasps, using the Iterated Closest Point (ICP) algorithm to align the coordinate frames of the depth maps~\cite{goldfeder2009data, goldfeder2011data}.
Kehoe et al.~\cite{kehoe2013cloud} created a Cloud-based system to transfer grasps evaluated by probability of force closure on objects in a database to a physical robot by indexing the objects with the Google Goggles object recognition engine.
Recent research has also studied grasp transfer from objects of the same category by warping contacts betwen corresponding points on a shape surface and using local rigid alignment and contact interpolation~\cite{hillenbrand2012transferring, stouraitis2015functional} or by interpolating grasps and shapes over a vector space representation called a Grasp Moduli Space~\cite{pokorny2014grasp, pokorny2013grasp}.

Another line of research focused on making analytic grasp metrics robust to imprecision in perception and control~\cite{goldberg1990bayesian, stulp2011learning, zheng2005}.
Brook, Ciocarlie, and Hsiao~\cite{brook2011collaborative, hsiao2011bayesian} developed a Bayesian framework to evaluate both the expected epsilon quality and the probability of physical success on a PR2 given uncertainty in object identity, object pose, and gripper positioning on deterministic mesh and point cloud models. 
Weisz et al.~\cite{weisz2012pose} found that grasps ranked by probability of force closure subject to perturbations of object pose in simulation were empirically more successful on a physical robot than grasps planned using deterministic WS metrics. 
Kim et al.~\cite{kim2012physically} planned grasps using the expected epsilon quality metric~\cite{ferrari1992} under dynamics and uncertainty in pose, and found that the robust metric has a higher correlation with physical grasp success.
Recent research has also studied grasping under object shape uncertainty resulting from imprecision of object segmentations in images~\cite{christopoulos2007handling}, part tolerancing in manufacturing~\cite{kehoe2012estimating, kehoe2012toward, panahi2015orienting}, or missing and noisy data from depth sensors such as the Kinect modeled with Gaussian process implicit surfaces~\cite{dragiev2013uncertainty, mahler2015gp, laskey2015bandits}.
%Many have also studied caging gripper configurations~\cite{rimon1996caging}, which are a waypoint to form closure grasps for two fingers~\cite{vahedi2008caging, rodriguez2012caging} and may be robust to perturbations in object pose and shape~\cite{diankov2008manipulation, Wan2012_ICRA}.

Recent research has also studied synthesizing grasps by ranking grasps according statistical models learned from human annotations or physical execution~\cite{bohg2014data}.
Saxena et al.~\cite{jiang2011efficient, saxena2008robotic} used a logistic regression classified to predict grasp affordances in images from human annotated training data.
Lenz et al~\cite{lenz2015deep} used deep learning to detect bounding boxes for parallel-jaw grasps in color and depth images, which was extended to real time by Redmon and Angelova~\cite{redmon2014real}.
Herzog et al.~\cite{herzog2012template, herzog2014learning} extracted "heightmaps" of local object curvature from human demonstrated grasps, construct a library of heightmap templates, and match new sensor data to templates to select grasps similar to the demonstrations.
Detry et al.~\cite{detry2012generalizing} created a low-dimensional representation of object parts and cluster object parts that are grasped similarly to form a shape library of prototypical grasp parts, and show that this representation can be transferred to real sensor data~\cite{detry2013learning}.
Kappler et al.~\cite{kappler2015leveraging} trained a deep neural network to predict grasp success for a Barett hand measured by human annotations and the results of simulations on a database of synthetic pointclouds of objects.
Deep learning~\cite{krizhevsky2012imagenet} has also ben used in robotics for learning visuomotor policies for specific manipulation tasks~\cite{levine2015end} and recurrent control policies for cutting fruits vegetables from joint angles and end-effector forces~\cite{lenzdeepmpc}.
%Recently, several other works have proposed to form a huge database of grasps on synthetic objects from simulation outcomes~\cite{michalikg3db} or physical execution~\cite{tellex}.
In comparison, we learn a model to predict a Bayesian distribution on the probability of force closure for a grasp on an object based on similarity to a set of prior grasps and objects in a database, and use our model to actively decide the next grasp to evaluate using Multi-Armed Bandits.

Our work is also closely related to research on actively selecting grasps for building a statistical model of grasp quality from fewer examples.
Several works have searched for successful grasps using belief space planning to minimze uncertainty~\cite{hsiao2007grasping, kahnactive, fischinger2015learning}, but without use of an explicit grasp quality metric to guide the search.
Kehoe et al.~\cite{kehoe2012estimating} proposed iterative pruning, an algorithm for evaluating the probability of force closure for a set of candidate grasps while discrading grasps known to have poor quality.
Detry et al.~\cite{detry2011learning} estimated a full continuous density function over grasp poses using kernel density estimation and adaptively acquired samples by pruning unsuccessful grasps.
Kroemer et al.~\cite{kroemer2010combining} developed a reinforcement learning approach to grasp selection based on seeding hypotheses via imitation learning and Gaussian process upper-confidence bounds for active grasp acquisition.
Boularias et al.~\cite{boularias2014efficient, boularias2015learning} used a Gaussian process Bayesian Optimization model for selecting grasps on cluttered piles of rocks.
Salaganicoff et al.~\cite{salganicoff1996active} used active learning to decide the next grasp to execute on a physical robot while learning a predicitve model of empirical success from range sensors.
Similarly, Montesano and Lopes~\cite{montesano2012active} used Continuous Correlated Beta Processes~\cite{goetschalckx2011continuous} to actively acquire grasp executions on a physical robot, measuring correlations from the responses to a bank of image filters designed to detect grasp affordances such as edges.
Recently, Laskey et al.~\cite{laskey2015bandits} showed that Multi-Armed Bandit (MAB) algorithms can be used to accelerate the identification of grasps with high probability of force closure under uncertainty in shape, pose, and friction in 2D.
MAB algorithms trade off gaining information about grasps that have been sampled fewer times with exploiting the grasp with the highest estimated quality given the past samples.
In this work we extend the model of Laskey et al.~\cite{laskey2015bandits} to 3D and to utilize similarity between grasps across objects from Dex-Net with CCBPs to further reduce the number of samples needed to converge to a grasp with high quality.

>>>>

%For a survey of the substantial literature on grasping, see Prattichizzo and Trinkle~\cite{prattichizzo2008grasping}.
Past research on grasp planning has focused on finding grasps by maximizing an analytic grasp quality metric based on a wrench space (WS), such as the ability to resist external perturbations to the object based on the grasp WS~\cite{ferrari1992, ciocarlie2009}, object WS~\cite{liu2015fast}, or task WS~\cite{kruger2011partial}.
%However, analytic WS metrics have been criticized~\cite{balasubramanian2012physical, weisz2012pose} for not being robust to variations in grasp acquistion, such as object shape, pose, material properties, and locations of contact~\cite{cheong2011output, diankov2010automated, weisz2012pose, zheng2005}.
However, the need to recompute WS metrics for every new object and grasp motivated research on grasp planning by transferring grasps from similar objects in a database of prior knowledge~\cite{li2005shape}.
%Li and Pollard~\cite{li2005shape} generated grasps for a human hand by matching object shapes to hand postures in a database.
Goldfeder et al.~\cite{goldfeder2009columbia} developed the Columbia grasp database, a dataset of 1,814 distinct models and over 200,000 force closure grasps generated using the Eigengrasp planner in GraspIt!~\cite{ciocarlie2009}.
The authors later used synthetic partial depth maps of objects in the database to match robot sensor data to precomputed grasps using the Iterated Closest Point algorithm~\cite{goldfeder2011data}.
Research has also studied transferring grasps from objects of the same category by warping contacts betwen corresponding points on a shape surface and using local alignment and contact interpolation~\cite{stouraitis2015functional} or by interpolating grasps and shapes over a vector space representation called a Grasp Moduli Space~\cite{pokorny2013grasp}.

Recent research has also studied labelling grasps in a database with metrics that are robust to imprecision in perception and control~\cite{brook2011collaborative, mahler2015gp, zheng2005}.
%, due to the fragility of analytic WS grasp metrics~\cite{balasubramanian2012physical, diankov2010automated, weisz2012pose}.
Weisz et al.~\cite{weisz2012pose} found that grasps ranked by probability of force closure subject to perturbations of object pose in simulation were empirically more successful on a physical robot than grasps planned using deterministic WS metrics. 
Similarly, Kim et al.~\cite{kim2012physically} planned grasps using the expected Ferrari-Canny quality~\cite{ferrari1992} under uncertainty in object pose using dynamic simulation to determine contacts, and found that the robust metric was more highly correlated with physical grasp success.
Kehoe et al.~\cite{kehoe2013cloud} created a Cloud-based system to transfer grasps evaluated by probability of force closure on objects in a database to a physical robot by indexing the objects with the Google Goggles object recognition engine.
The authors found that the full system of object recognition, pose estimation, and grasp execution successfully grasped objects on a table in 80\% of trials.

Another line of research has focused on synthesizing grasps using statistical models learned from a database of objects annotated with grasps decided by humans or physical execution~\cite{bohg2014data}.
Saxena et al.~\cite{jiang2011efficient, saxena2008robotic} used a logistic regression classified to predict grasp affordances in images from human annotated training data.
Lenz et al~\cite{lenz2015deep} used deep learning to detect bounding boxes for parallel-jaw grasps in color and depth images based on a dataset of thousands of 1035 images annotated with parallel-jaw grasps by humans.
Herzog et al.~\cite{herzog2012template, herzog2014learning} extracted heightmaps of local object curvature from human demonstrated grasps to construct a library of heightmap templates, and matched new sensor data to templates to select grasps similar to the demonstrations.
Detry et al.~\cite{detry2012generalizing} created a low-dimensional representation of object parts and cluster object parts that are grasped similarly to form a library of prototypical graspable point clouds, and showed that the representation could be transferred to real sensor data~\cite{detry2013learning}.
Kappler et al.~\cite{kappler2015leveraging} created a database of over 700 object instances each labelled with 500 Barrett hand grasps and their associated quality from human annotations and the results of simulations with the ODE physics engine.
The authors trained a deep neural network to predict grasp quality from heightmaps of the local object surface rendered along the surface normal. 
%Recently, several other works have proposed to form a huge database of grasps on synthetic objects from simulation outcomes~\cite{michalikg3db} or physical execution~\cite{oberlinacquiring}.
%Deep learning~\cite{krizhevsky2012imagenet} has also ben used in robotics for learning visuomotor policies for specific manipulation tasks~\cite{levine2015end} and recurrent control policies for cutting fruits vegetables from joint angles and end-effector forces~\cite{lenzdeepmpc}.
%Recently, several other works have proposed to form a huge database of grasps on synthetic objects from simulation outcomes~\cite{michalikg3db} or physical execution~\cite{tellex}.
In comparison, we learn a model to predict a belief distribution on the probability of force closure for a parallel-jaw grasp on a new object based on similarity to prior 3D objects and grasps, and we actively choose the next grasp to evaluate using Multi-Armed Bandits.

Our work is also closely related to research on actively selecting grasps for building a statistical model of grasp quality from fewer examples~\cite{boularias2015learning, salganicoff1996active}.
%Several works have searched for successful grasps using belief space planning to minimze uncertainty~\cite{hsiao2007grasping, kahnactive, fischinger2015learning}, but without use of an explicit grasp quality metric to guide the search.
Kehoe et al.~\cite{kehoe2012estimating} proposed iterative pruning, an algorithm for evaluating the probability of force closure for a set of candidate grasps while discarding grasps known to have poor quality.
Detry et al.~\cite{detry2011learning} estimated a full continuous density function over grasp poses using kernel density estimation and adaptively acquired samples by pruning unsuccessful grasps.
Kroemer et al.~\cite{kroemer2010combining} developed a reinforcement learning approach to grasp selection based on seeding hypotheses via imitation learning and Gaussian process upper-confidence bounds for active grasp acquisition.
%Boularias et al.~\cite{boularias2014efficient, boularias2015learning} used a Gaussian process Bayesian Optimization model for selecting grasps on cluttered piles of rocks.
%Salaganicoff et al.~\cite{salganicoff1996active} used active learning to decide the next grasp to execute on a physical robot while learning a predicitve model of empirical success from range sensors.
Montesano and Lopes~\cite{montesano2012active} used Continuous Correlated Beta Processes~\cite{goetschalckx2011continuous} to actively acquire grasp executions on a physical robot, measuring correlations from the responses to a bank of image filters designed to detect grasp affordances such as edges.
Recently, Laskey et al.~\cite{laskey2015bandits} used Multi-Armed Bandit (MAB) algorithms to reduce the number of samples needed to identify grasps with high probability of force closure under uncertainty in object shape, pose, and friction in 2D.
%MAB algorithms trade off gaining information about grasps that have been sampled fewer times with exploiting the grasp with the highest estimated quality given the past samples.
In this work we extend the model of Laskey et al.~\cite{laskey2015bandits} to 3D and to utilize similarity between grasps across objects from Dex-Net to further accelerate convergence to a grasp with high probability of force closure.

% DEEP LEARNING
Our work also builds on recent developments from the field of shape retrieval
\TODO{Let Matthieu provide initial version}

### 2015-09-10 ICRA2016/bandits_docs/paper.tex
Modified entire draft. In a limbo state. Going back through feedback now.

\begin{document}
\title{\LARGE \bf Dex-Net 1.0: A Cloud-Based Network of 3D Object Models Based on Deep Learning for Object Similarity and Multi-Armed Bandits for Robust Grasp Planning
%Correlated Multi-Armed Bandit Models for Large Scale 3D Grasp Planning Under Uncertainty
		\versionline{4}}
\author{Jeffrey Mahler$^1$, Florian Pokorny$^1$, Brian Hou$^1$, Mel Roderick$^1$, Michael Laskey$^1$, Kai Kohlhoff$^3$, \\ Torsten Kroeger$^3$, James Kuffner$^3$, Ken Goldberg$^2$
\thanks{$^1$Department of Electrical Engineering and Computer Sciences; {\tt\small \{jmahler, ftpokorny, brian.hou\}@berkeley.edu, melrose\_roderick@brown.edu}}%
\thanks{$^2$Department of Industrial Engineering and Operations Research; {\tt\small goldberg@berkeley.edu}}%
\thanks{$^{1-2}$ University of California, Berkeley, USA}%
\thanks{$^3$ Google Inc., Mountain View, USA; {\tt\small \{kohlhoff, tkr, kuffner\}@google.com}}
}
\maketitle

\TODO{Possibly will include Matthieu Aubry, Alyosha Efros, and Pieter Abbeel as coauthors} \\
\TODO{Update number of models in title: I want it to reflect exactly how many we use in experiments}

\input{includes/abstract}
%
\input{includes/introduction}
\input{includes/related_work}
%
\input{includes/problem_statement}
\input{includes/background}
\input{includes/algorithm}
\input{includes/dataset}
\input{includes/experiments}
\input{includes/conclusion}

@@

>>>>

\begin{document}
\title{\LARGE \bf Dex-Net 1.0: A Cloud-Based Network of 3D Objects and Parallel-Jaw Grasps and a Multi-Armed Bandit Algorithm with Correlated Rewards for Robust Grasp Planning at Scale
%Correlated Multi-Armed Bandit Models for Large Scale 3D Grasp Planning Under Uncertainty
		\versionline{4}}
\author{Jeffrey Mahler$^1$, Florian Pokorny$^1$, Brian Hou$^1$, Melrose Roderick$^1$, Michael Laskey$^1$, Matthieu Aubry$^1$, \\
Kai Kohlhoff$^3$, Torsten Kroeger$^3$, James Kuffner$^3$, Ken Goldberg$^2$
\thanks{$^1$Department of Electrical Engineering and Computer Sciences; {\tt\small \{jmahler, ftpokorny, brian.hou\}@berkeley.edu, melrose\_roderick@brown.edu}}%
\thanks{$^2$Department of Industrial Engineering and Operations Research; {\tt\small goldberg@berkeley.edu}}%
\thanks{$^{1-2}$ University of California, Berkeley, USA}%
\thanks{$^3$ Google Inc., Mountain View, USA; {\tt\small \{kohlhoff, tkr, kuffner\}@google.com}}
}
\maketitle

%\TODO{Possibly will include Matthieu Aubry, Alyosha Efros, and Pieter Abbeel as coauthors} \\
%\TODO{Update number of models in title: I want it to reflect exactly how many we use in experiments}

\input{includes/abstract}
%
\input{includes/introduction}
\input{includes/related_work}
%
\input{includes/problem_statement}
\input{includes/dataset}
%\input{includes/background}
\input{includes/algorithm}
\input{includes/experiments}
\input{includes/conclusion}

@@

\section{Acknowledgments}
This research was performed with UC Berkeley's Automation Sciences Lab under the UC Berkeley Center for Information Technology in the Interest of Society (CITRIS) "People and Robots" Initiative: http://robotics.citris-uc.org.
The authors were supported in part by the U.S. National Science Foundation under NRI Award IIS-1227536, and by grants from Google, Cisco, and UC Berkeley's Algorithms, Machines, and People Lab.
We thank our colleagues who wrote code for the project, in particular Raul Puri, Sahanna Suri, Nikhil Sharma, and Josh Price, as well as our colleagues who gave feedback and suggestions, in particular Pieter Abbeel, Matthieu Aubry, Alyosha Efros, Animesh Garg, Kevin Jameison, Sanjay Krishnan, Zoe McCarthy, Stephen McKinley, Sachin Patil, Nan Tian, and Jur van den Berg.
